---
title: "The Effects of Clean Beauty Labels on Customer Purchase Behavior at Sephora"
author:  "Maya Patel, Tess Ibrahimchah, Sara Shreim, Suhasini Singh, & Depali Kulkarni"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment="", warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)

# Make sure to change the name of the file to something more descriptive for your project.
```

## Part 1:  Research Proposal

### Memo to Decision Makers

**Authors (Names and Percentages)**: Maya Patel (100%)

  The beauty industry is an evolving work space that is constantly shifting to meet market needs and trends. Recently, consumers have been shifting their focus on “clean-beauty” products which is when beauty and skin care brands focus their products on having non-toxic ingredients, environmentally safe packaging, and cruelty-free testing in order to ensure transparency between the company and its consumer. Shifting to this new standard for products is not only safer for the customer and environment, but also could have monetary benefits for beauty companies as consumers may gravitate towards these products versus competitor products. Understanding how consumers interact with clean beauty products will help the cosmetic industry facilitate how they create their products and develop marketing strategies in order to increase profitability. Reputation and establishing consumer loyalty is vital to the longevity of a company in this industry as it will lead to brand popularity as well as increase in repeat purchases. Ensuring transparency as well as shifting focus on climate impact and ingredients established a connection between the business and consumer, allowing customers to understand the company's main focus is creating valued products instead of profitability.
  
  In this study we will focus on one marketing technique, clean - beauty product labels on the Merit beauty packaging, to understand consumer behavior. The research conducted will test the following product packaging labels: no-label, “non-toxic”, and “sustainable - packaging” against customers' engagement with the email advertisement as well as the sales conversion between these product labels. Once the emails are sent out, systematic data collection will occur measuring whether the beauty insider customer clicked on the ad and if that click through converted to a sales. From this analysis Merit beauty will be able to focus their product packaging on labels that adhere to a rise in customer interaction, expand brand recognition, and increase profitability. 
  
  The sephora beauty insider customer database will be used to randomly select consumers in the three age groups selected for an email marketing research study. The sample will be systematically selected so that it is equally distributed between the age groups as well as the three different email types. These email types will display a Merit beauty product each with different packaging labels which are no label, non-toxic, and sustainable packaging. Once the sample is chosen and the product pages have been created we will draft identical emails for all consumers, only changing the specific “clean-beauty” label mentioned above. The emails will be sent out and the data collection will begin, studying if the email link was clicked, how long the customer remained on the products page, as well as if the advertisement click was converted into a product purchase. The final analysis will include all these data points cross referenced between the various age groups as well as gender. The final findings will help Merit beauty and other beauty brands sold at sephora make data driven decisions to maximize their revenue and brand reputation through changes in their product formulas, packaging material, and brand transparency. 


### Statement of the Problem

**Authors (Names and Percentages)**: Tess Ibrahimchah (100%)

  The beauty industry is a billion dollar business that is constantly innovating. In recent times, and with the rise of sustainable awareness, we can see the emerging trend of “clean-beauty”. Clean beauty serves as an umbrella-term encompassing multiple areas; such as non-toxic ingredients, environmental safety, cruelty-free testing and business-to-consumer transparency. The idea of clean beauty emphasizes the importance of transparency to consumers, in order for buyers to feel safe and informed while making decisions on the products they use on their body while also being environmentally friendly and ethical. Merit, is a new beauty brand that values and produces clean-beauty products. Merit Beauty is looking to stand out in an oversaturated market, with a lot of established and new emerging brands clinging to this opportunity of clean beauty such as Ilia beauty, Saie, Kosas, RMS beauty etc. Marketing plays a huge role in helping a brand distinguish itself and communicate its values with an engaging brand image. Thus, it is important to study the effects of certain marketing avenues to see what is efficient and worth allocating resources towards. Different marketing strategies include social media marketing, influencer marketing, text message marketing, e-mail marketing etc. In this study, we will be looking at the clean beauty brand “Merit” and the effects different clean-beauty labels have on sales behavior. Merit is largely sold at Sephora, which is the world's leading beauty retailer with a large range of beauty brands. We will be collecting our data from Sephora email ads (concerning Merit) to Sephora subscribers. Since product labeling plays a big role in brand marketing and heavily impacts sales, we will be able to see how clean-beauty labels will affect consumers interests and purchasing rates. This study will show that clean and sustainable products are not only beneficial to the environment but could also be used as a profitable business strategy. This study will help Merit create a focused and data-driven strategy to increase consumers’ interest and drive sales.  In conclusion, clean beauty shows benefits for the environment, for consumers’ health, and for profit. Therefore, it is important for a brand such as Merit to see how to leverage these advantages to reach its full business potential. 


### Literature Review

**Authors (Names and Percentages)**: Depali Kulkarni (100%)

  Clean beauty is increasingly more popular among Millennials and Gen Z, who prioritize safe, ethical, and environmentally friendly products. Publications on clean beauty indicate that product description and eco-friendly marketing have a significant influence on consumer opinion and purchase intention (Mou, Zhu, & Benyoucef, 2019). Particularly, absence-framed assertions (for example, "paraben free") result in a more positive attitude than presence-framed claims (for example, "with avocado oil") (Grappe, Lombart, Louis, & Durif, 2022). 
  
  Overall, Gen Z demonstrates a stronger preference for clean beauty than older generations (Shim et al., 2024). Additionally, a preference for clear certification labels over detailed ingredient lists is seen (Lavuri et al., 2022). 
  
  However, these studies face limitations. Many are based on relatively small sample sizes and rely on self-reported values. When studies depend on self-reported data, they may be subject to biases such as social desirability bias. This distorts the accuracy of data. There is also often a gap between preferences and actual purchases that may arise from financial constraints or marketing influences. Convenience sampling methods, where consumers are chosen based on their availability rather than being randomly selected, further distort the findings. Demographic biases add new complexities. These limitations highlight the need for broader research. 


### Research Questions, Hypotheses, and Effects
**Authors (Names and Percentages)**: Maya Patel (50%) & Sara Shreim (50%)

*Research Question 1:* Relative to the average sales of a non labeled product, do the clean labels “non-toxic” and “sustainable packaging” increase the average rate of sales of the Merit beauty product among Sephora users?

   1. Null Hypothesis: Clean labels have no effect on the sales rate compared to the non-labeled beauty product.
   
   2. Alternative Hypothesis: Clean labels increase the sales rate compared to the non-labeled beauty product.

*Research Question 2:* Relative to the average sales of a non labeled product, which age group of Sephora users are more likely to purchase a clean beauty product with the labels “non-toxic” or “sustainable packaging”?

   1. Null Hypothesis: There is no significant relationship between age groups and the effect on sales when it comes to buying a beauty product with the clean labels, “non-toxic” and “sustainable packaging”.
   
   2. Alternative Hypothesis: There is a significant relationship between age groups and the effect on sales when it comes to the likelihood of buying a beauty product with the clean labels, “non-toxic” and “sustainable packaging”. 

*Research Question 3:* Relative to a non-labeled product, is there a relationship between click through rates and sales behavior on beauty products with the clean beauty labels of “non-toxic” or “sustainable packaging”? 

   1. Null Hypothesis: There is no significant relationship between click through rates and sales behavior on beauty products with the clean beauty labels “non-toxic” or “sustainable packaging” . 
   
   2. Alternative Hypothesis: There is a positive relationship between click through rates and sales behavior on beauty products with the clean beauty labels “non-toxic” or “sustainable packaging”.  

For research question 1 the minimum effect size should be a 15% increase in sales for the Merit product based on the label that most adheres with customers intent to purchase. For research question 2 the minimum effect size is Generation Z is 30% more likely to purchase the product with clean beauty labels compared to the other 2 age groups. Lastly, research question 3 has a minimum effect size of a 25% increase in the likelihood of purchasing the product if the user clicks on it. This would justify the cost of the added detail to the product’s packaging, as well as the marketing campaigns that could be implemented to expand the Merit’s target demographic and increase sales.  



### Importance of the Study and Social Impact

**Authors (Names and Percentages)**: Tess Ibrahimchah (100%)

Our study will allow the company Merit Beauty to increase its engagement and sales, and in turn possibly the products profitability. This is because the study looks at the effectiveness of different email-marketing strategies pertaining to product labels. This will allow Merit to see if this strategy is worth allocating its resources, time and money, towards this relatively simple and low-cost strategy. Moreover, the study will evaluate if the outcome of utilizing these labels can reinforce its brand image and values to unleash its full business potential. In addition, this could help the brand optimize its strategy even outside Sephora. Furthermore, the use of descriptive clean-beauty labels not only allows Merit to convey its philosophy, but allows consumers to genuinely make informed decisions and learn about clean beauty if unfamiliar with it. Moreover, if these strategies prove themselves to be beneficial, this could encourage other brands to incorporate clean beauty techniques which will help the environment and consumer health on a bigger spectrum. This is important on a global level as ingredient safety and environmental concerns / sustainability are big topics of concern that are worsening with time.


### Research Plan

#### Population of Interest

**Authors (Names and Percentages)**: Tess Ibrahimchah (50%) & Suhasini Singh (50%)

The population of interest for this study consists of existing Sephora customers who are subscribed to Sephora's email newsletters. Specifically, we are targeting makeup consumers aged 16 to 60, aligning with Sephora's customer profile and the broader beauty industry's demographic. Three distinct email labels will be developed and sent to participants across three different generational groups: Gen Z (16-24), Millennials (25-40), and Gen X (41-60). Generational age group response helps to identify which generational segments (Generation Z, Millennials, and Generation X) are most responsive to clean beauty labels.


#### Sample Selection

**Authors (Names and Percentages)**: Maya Patel (50%) & Suhasini Singh (50%)

The sample is randomly selected from the Sephora rewards customer database, where equal numbers of each age group: Gen Z (16-24), Millennials (25-40), and Gen X (41-60) are chosen to receive the email campaign.  Each age group is subdivided into three equal groups representative of the different email types, “no label”, “non-toxic”, and “sustainable packaging”. The inclusion criteria for this study includes being a part of the Sephora rewards program and the qualifying age groups. If a specified spending tier was included in the inclusion criteria, this could skew our data as their spending habits could create bias towards the brand or overall purchase behavior at Sephora. This vast and diverse sample will give a robust data set that ensures an equal distribution of customers and spending habits.


#### Operational Procedures

**Authors (Names and Percentages)**: Maya Patel (33%),  Tess Ibrahimchah (33%), & Sara Shreim (33%)

To establish a fully randomized sample, we will start by reaching out to 450 Sephora customers, randomly selected from those subscribed to Sephora's rewards program. When each customer signs up for a Sephora account they are prompted to read and agree to the terms and condtions of the rewards program, which states they give informed consent to participate in any studies or research conducted on the platform or via communication provided. From the 450 Sephora customers contacted, equal representation across the generational groups will be ensured, approximately 150 from the following Gen Z, Millennials, and Gen X. 

We then create three distinct advertisements for the beauty product. The first advertisement will serve as a control and contain no additional verbiage. The second advertisement will feature the phrase “Non-Toxic Ingredients,” while the third will include the label “Sustainable Packaging.” Using the Sephora Beauty Insider database, we will distribute these advertisements via targeted emails to our randomly selected sample group. 

Staff will be trained to follow the randomization protocol to assign participants to groups randomly, without any bias. The staff responsible for monitoring and recording CTR and sales data will be trained on using the software tools provided by Sephora’s marketing and analytics team. The recruitment process will take one week, the advertisement will be sent out within one week of recruitment closure, data will be collected over a two-week period and will be analyzed for a week after data collection is complete.

Participants will receive all communication via email, there will be no direct or in-person interaction with the study staff, which ensures anonymity and minimizes bias. One Follow-up email will provide reminders to check the advertisement and complete any other necessary actions. No personally identifiable information will be collected, ensuring data privacy, and all data collected will be stored securely with only aggregate results being reported. All participants will be informed of their right to withdraw from the study at any time with no explanation needed and with no consequence. There will be an opt-out link provided in all communication emails.

Participants who might participate in the study would be regular Sephora customers who are interested in learning more about clean beauty research and are motivated by their curiosity or shifting their beauty life to cleaner beauty. Individuals who might not participate in this study would be those who are uninterested in clean beauty products. 


#### Brief Schedule

**Authors (Names and Percentages)**: Depali Kulkarni (70%) & Suhasini Singh (30%) 

Weeks 1 and 2 will consist of participant selection and the launch of the email campaign. The project will begin with the random selection of participants from the Sephora Beauty Insider database as per the three generational age categories - Generation Z, Millennials and Generation X. This ensures to remove bias and that the sample is representative of the broader customer base. The selected participants will then receive targeted emails promoting products with 3 different clean beauty labels. During this time, participant behavior will be continuously tracked and recorded. The key performance metrics will include click-through rates (CTR) that measure the effectiveness of the email content in prompting engagement from the customers, sales conversions tracking whether email recipients make purchases, as influenced by the clean beauty labels, and time measuring the amount of minutes a consumer spends on the specific product page using the link in the email. 

Week 3 will focus on  data cleaning, categorization and statistical analysis. During this, data collected will undergo a data cleaning and the preparation phase. This will include addressing all of missing or inaccurate values by filling in gaps or excluding problematic entries and organizing data based on age groups, labels they were exposed to, click through rate, the final sales outcome and time measurement. Once cleaned and categorized, data will be analyzed using a variety of statistical methods to test the hypotheses. Lastly, insights will be derived on the effectiveness of clean beauty labels.  The specific analysis will include: T-tests, Chi-square tests, and Regression models. Through these tests, the team will be able to determine whether the clean beauty labels positively impact purchasing decisions and whether certain age groups are more likely to be influenced by the labeling. 


#### Data Collection

**Authors (Names and Percentages)**: Maya Patel (100%) 

When a consumer signs up for a sephora rewards account they are prompted to read and accept the terms and conditions of the program. The terms and conditions state they agree to all marketing campaigns and research studies, allowing sephora to collect their data if randomly selected to participate. Once the selected sample is chosen from the age groups selected, the three email types are sent and the data collection will begin. We will track if the consumer clicks on the three email types and compares those values against the other individuals in the specific email label group. Of the consumers who clicked on the product via email, we will track if that interaction converted to a sale of the product. We will also track the amount of time spent on the products page once clicking the link from the email, this will be used for secondary analysis to understand consumer engagement with the products visual perception. 



#### Data Security

**Authors (Names and Percentages)**: Depali Kulkarni (100%) 


While analyzing purchase decisions and tracking participant behavior, it is important to maintain high standards of customer data security. Ensuring that personal and transactional data remains secure is a legal and ethical obligation. It also helps maintain customer trust and the firm’s reputation. The following strategies will help the team keep customer data secure during the experimentation. Data Encryption will consist of converting sensitive data such as communications into an unreadable format, which needs to be decoded with an encryption key. The study will ensure compliance with the data protection regulation as well as, secure payment processing Gateways to offer secure processing of transactions. Lastly to ensure security, access Control will be initiated assigning roles based on access to ensure that only authorized personnel have access to sensitive customer data and auditing to help  detect unusual and suspicious activities that can escalate to potential breaches. 


#### Variables


##### Outcomes (Dependent Variables)


**Authors (Names and Percentages)**: Sara Shreim (100%) 

This study focuses on three main dependent variables that measure the impact of clean beauty labels on consumer behavior. The first dependent variable is sales conversion. Sales conversion refers to whether the participant purchases the product after engaging with the email advertisement of the product. This variable will tell us the effectiveness of  the clean beauty label by matching it to the actual consumer purchasing behavior. This variable measurement will have a binary outcome: either yes, the participant bought the product or no, the participant did not buy the product. 

The second dependent variable is the click-through rate (CTR). The CTR measures the proportion of participants who clicked on the advertisement link in the email, taking them from their email to the Sephora product site page, indicating that they are interested in the product. This variable measurement is continuous, with CTR being the number of clicks divided by the total number of emails delivered multiplied by 100. A higher CTR would suggest a stronger consumer engagement. Even though this does not lead to an immediate purchase of the product, this variable will show us the consumers initial interest in clean beauty labeled products. 

The last dependent variable is the age group response. We plan to analyze the effectiveness of clean beauty labels on sales and CTR across three generational groups: Gen-Z (ages 16-24), Millennials (ages 25-40) and Gen-X (ages 41-60). Each participant will provide their age at the time of study enrolment. The variable will be analyzed in relation to sales conversion and CTR to identify any generational differences in response to clean beauty products. This variable will help us determine which demographic is most influenced by clean beautify labels which will guide future targeted marketing strategies. 


##### Treatments (Independent Variables)

**Authors (Names and Percentages)**: Tess Ibrahimchah (100%)

  The first group is the control group that will serve as our baseline group to make comparisons with the two other groups. This group will have no label. The second group, our first treatment group, will have a “Non-Toxic Ingredients” label. And the third group, the second treatment group, will have a “Sustainable Packaging” label. For all the cohorts, we will look at their age groups: Gen Z, Millennials,  or Gen X. All the groups will be randomly assigned for the randomly chosen sample of Sephora customers newsletter subscribers. 



##### Other Variables

**Authors (Names and Percentages)**: Tess Ibrahimchah (50%) & Sara Shreim (50%)

Besides the independent and dependent variables, there may be other variables that influence the outcomes of the study, making them relevant for analysis. The other variables are gender and prior purchase history. Gender would be listed as male, female, or prefer not to say. This would help us identify differences in the impact of clean beauty labels across genders. Prior purchase history is if the participant has purchased a Merit product before. This variable will help us control for pre-existing brand loyalty/familiarity which could affect sales behavior and CTR.



### Statistical Analysis Plan  

**Authors (Names and Percentages)**: Sara Shreim (100%) 

In order to answer our research questions, we must run multiple statistical tests. For our first question, we will be performing a two sample t-test to compare the mean sales rates between our clean-labeled products and our unlabeled product, where our H0: μclean labels​=μnon-labeled, and Ha: μclean labels​>μnon-labeled​​. For our second question, we will run a chi-square test of independence to assess if there is a statistically significant association between age group and purchase behavior for clean-labeled versus unlabeled products, where our H0: μAge Group 1​=μAge Group 2​=…=μAge Group 4, and our Ha: μAge Group n​ does not equal at least one μAge Group. For our third question, we will run a regression analysis to see if there is a linear relationship between click through rates and sales on our clean-labeled products. Once we have compiled the data, we will be summarizing it into the mean, median and standard deviation. Our significance level for all three tests will be an alpha of 0.05, where a p-value below our alpha will result in rejecting the null hypothesis in favor of the alternative hypothesis. 


### Sample Size and Statistical Power

**Authors (Names and Percentages)**: Maya Patel (50%) & Suhasini Singh (50%)


```{r }
library(pwr)

# Define the parameters
p1 <- 0.30  # Conversion rate for No Label (baseline)
p2 <- 0.45  # Conversion rate for Clean Label (15% increase)

# Compute the effect size (Cohen's h)
effect_size <- ES.h(p1, p2)

# Conduct power analysis for two-proportion test
sample_size <- pwr.2p.test(h = effect_size, 
                           n = NULL,   # We want to calculate the sample size
                           sig.level = 0.05, 
                           power = 0.80, 
                           alternative = "two.sided")

# Print the calculated sample size per group
sample_size

pwr.chisq.test(w = 0.30 ,
               df = 2,   # degrees of freedom (calculated earlier)
               sig.level = 0.05, 
               power = 0.80)

pwr.f2.test(u = 1,  # Number of predictors (1 for Ad Clicked)
            f2 = 0.25,  # Cohen's f^2 for medium effect size
            sig.level = 0.05, 
            power = 0.80)
```

The minimum sample size for research question 1 was calculated using 80% power to produce a minimum effect of a 15% sales increase compared to the baseline 30% sales conversion. The sample size is 162 customers for one group, thus a total sample size for labeled and non-labeled products would be 324. For research question 2 a pwr.chisq.test was conducted using the same effect size and 2 degrees of freedom, (df=(3−1)(2−1)=2.), as there are 3 age groups being compared to 2 behaviors, purchased and not purchased. This produced a sample size of 108 customers. Lastly, for research question 3 a pwr.f2.test was run with 1 predictor, if the ad was clicked, and the effect size of a 25% increase in the likelihood of purchasing the product if the user clicks on it with the same power. The sample size calculated was 32 individuals which is the lowest of the 3 test run. In order to increase statistical power and the likelihood of our hypothesis testing having the true effect we will use a sample size of 450 customers. This number can be equally divided by the 3 age demographics as well as subdivided into the 3 email treatments. 



### Possible Recommendations

**Authors (Names and Percentages)**: Sara Shreim (100%)

*Research Question 1:* Relative to the average sales of a non labeled product, do the clean labels “non-toxic” and “sustainable packaging” increase the average rate of sales of the Merit beauty product among Sephora users?

   1. Recommendation if null hypothesis is not rejected: If the data shows that clean beauty labels do not significantly increase sales then the company should avoid incurring additional costs for implementing clean beauty labels in product design and packaging. Instead, the company should focus on alternative marketing strategies. 

   2. Recommendation if null hypothesis is rejected: If the data shows that clean beauty labels significantly increase sales, then the company should prioritize incorporating these labels into more Merit products to maximize consumer interests and sales. The company should also develop more marketing campaigns to highlight the brand's clean beauty feature and focus on its commitment to sustainability and transparency. 

*Research Question 2:* Relative to the average sales of a non labeled product, which age group of Sephora users are more likely to purchase a clean beauty product with the labels “non-toxic” or “sustainable packaging”?

   1. Recommendation if null hypothesis is not rejected:
If the data shows that there is no significant relationship between age group and purchase behavior, then the company should use a general approach and market the clean beauty product broadly across all age groups.

   2. Recommendation if null hypothesis is rejected:
If the data shows that there is a significant relationship between age group and purchase behavior, then the company should focus on tailoring marketing strategies to target those specific age groups.

*Research Question 3:* Relative to a non-labeled product, is there a relationship between click through rates and sales behavior on beauty products with the clean beauty labels of “non-toxic” or “sustainable packaging”? 

   1. Recommendation if null hypothesis is not rejected: If the data shows that click-through rates are not significantly correlated with sales, then the company should focus on other channels of advertising such as in-store promotions or influencer marketing to drive sales. The company should also re-design their email marketing to better align with customers' purchasing behavior.

   2. Recommendation if null hypothesis is rejected: If the data shows that click-through rates are significantly correlated with sales, then the company should invest more in email marketing campaigns to achieve a higher CTR. This could allow the company to use CTR as a key metric in evaluating the effectiveness of future marketing campaigns.


### Limitations and Uncertainties

**Authors (Names and Percentages)**: Suhasini Singh (100%)

  This study is subject to several limitations and uncertainties that could impact the interpretation of its results. First, the sample size is based on assumptions about baseline conversion rates and the expected effects of clean beauty labels. While these assumptions were informed by prior studies and a rigorous power analysis, real-world variability in consumer behavior could lead to deviations from these estimates. Additionally, the study assumes that all purchases made during the research timeframe are directly attributable to the advertisements, which may not account for external influences such as prior brand exposure, personal preferences, or competing marketing campaigns.

  Another limitation lies in the distribution of participants across generational groups and traffic sources. While efforts were made to ensure randomization and proportional representation, biases in engagement levels across age groups or traffic sources (e.g., ads versus organic search) could affect the results. Moreover, the effectiveness of advertisements with clean beauty labels is likely influenced by factors not captured in this study, such as the aesthetic appeal of the ad, the pricing of products, or seasonal variations in consumer spending.
  
  Future research could address these uncertainties by expanding the scope of the study to include a larger and more diverse sample, allowing for deeper insights into demographic-specific preferences. Longitudinal studies could also be conducted to evaluate the sustained impact of clean beauty labels on consumer loyalty and repeat purchases. Additionally, integrating qualitative methods, such as surveys or interviews, could provide a richer understanding of consumer motivations and perceptions. By addressing these limitations and exploring new directions, future research can build a more comprehensive framework for understanding the role of clean beauty labels in influencing purchasing behavior.



## Part 2:  Simulated Studies

**Authors (Names and Percentages)**: Maya Patel (70%) & Sara Shreim (30%)



### Research Question 1:

*Research Question 1:* Relative to the average sales of a non labeled product, do the clean labels “non-toxic” and “sustainable packaging” increase the average rate of sales of the Merit beauty product among Sephora users?

#### Scenario 1:  No Effect

   1. Null Hypothesis: Clean labels have no effect on the sales rate compared to the non-labeled beauty product.

##### Analysis

##### Simulation

```{r q1_scenario1_simulation}

# Load required libraries
library(dplyr)
library(knitr)
library(kableExtra)

# Set seed for reproducibility
set.seed(1031)

# Function to simulate sales data (clean vs non-labeled)
simulate_sales_data <- function(effect_size = 0, n = 450) {
  # Simulate sales for non-labeled and clean-labeled products
  non_labeled <- rnorm(n, mean = .150, sd = .10)  # Non-labeled sales
  clean_label <- rnorm(n, mean = .150 + (effect_size), sd = .10)  # Clean-labeled sales with effect size
  
  # Perform a two-sample t-test (we'll use t-test for simplicity here)
  t_test_result <- t.test(clean_label, non_labeled, alternative = "greater")
  
  # Effect size as the mean difference
  effect <- mean(clean_label) - mean(non_labeled)
  
  return(list(effect_size = effect, p_value = t_test_result$p.value))
}

# Run simulations
run_simulations <- function(effect_size, n_sims = 1000) {
  results <- replicate(n_sims, simulate_sales_data(effect_size), simplify = FALSE)
  
  # Extract effect sizes and p-values from simulation results
  effects <- sapply(results, function(x) x$effect_size)
  p_values <- sapply(results, function(x) x$p_value)
  
  # Calculate results
  list(
    mean_effect = mean(effects),
    ci_lower = quantile(effects, 0.025),
    ci_upper = quantile(effects, 0.975),
    false_positives = if (effect_size == 0) mean(p_values < 0.05) * 100 else NA,
    true_negatives = if (effect_size == 0) mean(p_values > 0.05) * 100 else NA,
    false_negatives = if (effect_size != 0) mean(p_values > 0.05) * 100 else NA,
    true_positives = if (effect_size != 0) mean(p_values < 0.05) * 100 else NA
  )
}

```

##### Analysis

```{r q1_scenario1_analysis}

null_results <- run_simulations(effect_size = 0)        # No effect scenario

```


#### Scenario 2:  An Expected Effect

   2. Alternative Hypothesis: Clean labels increase the sales rate compared to the non-labeled beauty product.

##### Analysis

```{r q1_scenario2_analysis}
effect_results <- run_simulations(effect_size = 0.15)  # 15% increase scenario

# Create results table
results_table <- tibble(
  `Research Question` = c("Question 1", "Question 1"),
  Scenario = c("No Effect", "Effect: 15% Increase in Sales"),
  `Mean Effect in Simulated Data` = c(
    sprintf("%.2f", null_results$mean_effect),
    sprintf("%.2f", effect_results$mean_effect)
  ),
  `95% Confidence Interval of Mean Effect` = c(
    sprintf("(%.2f, %.2f)", null_results$ci_lower, null_results$ci_upper),
    sprintf("(%.2f, %.2f)", effect_results$ci_lower, effect_results$ci_upper)
  ),
  `Percentage of False Positives` = c(
    sprintf("%.1f%%", null_results$false_positives),
    "N/A"
  ),
  `Percentage of True Negatives` = c(
    sprintf("%.1f%%", null_results$true_negatives),
    "N/A"
  ),
  `Percentage of False Negatives` = c(
    "N/A",
    sprintf("%.1f%%", effect_results$false_negatives)
  ),
  `Percentage of True Positives` = c(
    "N/A",
    sprintf("%.1f%%", effect_results$true_positives)
  )
)

# Display the results table
kable(results_table, caption = "Simulation Results for Research Question 1", align = "c") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```



### Research Question 2:

*Research Question 1:* Relative to the average sales of a non labeled product, do the clean labels “non-toxic” and “sustainable packaging” increase the average rate of sales of the Merit beauty product among Sephora users?

#### Scenario 1:  No Effect

1. Null Hypothesis: There is no significant relationship between age groups and the effect on sales when it comes to buying a beauty product with the clean labels, “non-toxic” and “sustainable packaging”.

##### Simulation

```{r q2_scenario2_simulation}
# Load required libraries
library(dplyr)
library(knitr)
library(kableExtra)

# Set seed for reproducibility
set.seed(12)

simulate_and_test_age_data <- function(effect_size = 0.0, n = 450) {
  # Number of individuals per age group (approximately equal split)
  gen_z_size <- floor(n * 0.33)
  millennials_size <- floor(n * 0.33)
  gen_x_size <- n - gen_z_size - millennials_size  # Ensure exact total
  
  # Purchase probabilities: Gen Z has 30% more chance to purchase than others
  purchase_prob <- c("Gen Z" = 0.250 + effect_size, 
                     "Millennials" = .250, 
                     "Gen X" = 0.250)
  # Simulate purchases for each group
  gen_z_purchase <- rbinom(gen_z_size, 1, purchase_prob["Gen Z"])
  millennials_purchase <- rbinom(millennials_size, 1, purchase_prob["Millennials"])
  gen_x_purchase <- rbinom(gen_x_size, 1, purchase_prob["Gen X"])
  
  # Combine all into a single data frame
  data <- data.frame(
    age_group = c(rep("Gen Z", gen_z_size), 
                  rep("Millennials", millennials_size), 
                  rep("Gen X", gen_x_size)),
    purchase = factor(c(gen_z_purchase, millennials_purchase, gen_x_purchase))
  )
  
  # Create a contingency table
  table_data <- table(data$age_group, data$purchase)
  
  # Perform the Chi-Square test
  chi_sq_result <- chisq.test(table_data)
  
  # Return the p-value from the test
  return(list(
    chi_sq_p_value = chi_sq_result$p.value,
    data = data
  ))
}
  
```

##### Analysis

```{r q2_scenario1_analysis}
null_results <- run_simulations(effect_size = 0)        # No effect scenario
```



#### Scenario 2:  An Expected Effect

2. Alternative Hypothesis: There is a significant relationship between age groups and the effect on sales when it comes to the likelihood of buying a beauty product with the clean labels, “non-toxic” and “sustainable packaging”. 

##### Analysis

```{r q2_scenario2_analysis}

effect_results <- run_simulations(effect_size = 0.30)  # 30% increase scenario

# Create results table
results_table <- tibble(
  `Research Question` = c("Question 2", "Question 2"),
  Scenario = c("No Effect", "Effect: Gen Z is 30% More Likely to Purchase"),
  `Mean Effect in Simulated Data` = c(
    sprintf("%.2f", null_results$mean_effect),
    sprintf("%.2f", effect_results$mean_effect)
  ),
  `95% Confidence Interval of Mean Effect` = c(
    sprintf("(%.2f, %.2f)", null_results$ci_lower, null_results$ci_upper),
    sprintf("(%.2f, %.2f)", effect_results$ci_lower, effect_results$ci_upper)
  ),
  `Percentage of False Positives` = c(
    sprintf("%.1f%%", null_results$false_positives),
    "N/A"
  ),
  `Percentage of True Negatives` = c(
    sprintf("%.1f%%", null_results$true_negatives),
    "N/A"
  ),
  `Percentage of False Negatives` = c(
    "N/A",
    sprintf("%.1f%%", effect_results$false_negatives)
  ),
  `Percentage of True Positives` = c(
    "N/A",
    sprintf("%.1f%%", effect_results$true_positives)
  )
)

# Display the results table
kable(results_table, caption = "Simulation Results for Research Question 2", align = "c") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))


```



### Research Question 3:

*Research Question 3:* Relative to a non-labeled product, is there a relationship between click through rates and sales behavior on beauty products with the clean beauty labels of “non-toxic” or “sustainable packaging”? 

#### Scenario 1:  No Effect

   1. Null Hypothesis: There is no significant relationship between click through rates and sales behavior on beauty products with the clean beauty labels “non-toxic” or “sustainable packaging” . 
   
##### Simulation

```{r q3_scenario1_simulation}
## Load required libraries
library(dplyr)
library(knitr)
library(kableExtra)

# Set seed for reproducibility
set.seed(1256)

# Function to simulate CTR and sales data and perform linear regression for Research Question 3
simulate_ctr_sales_lm <- function(effect_size = 0.25, n = 450) {
  # Simulate CTR (Click-Through Rates)
  ctr <- rnorm(n, mean = 0.2, sd = 0.5)  # Simulated click-through rates
  
  # Simulate Sales based on CTR with some added noise
  sales <- .2 + effect_size * ctr + rnorm(n, mean = .2, sd = 0.5)  # Simulated sales based on CTR
  
  # Create data frame for regression
  data <- data.frame(ctr = ctr, sales = sales)
  
  # Perform linear regression (sales ~ ctr)
  lm_model <- lm(sales ~ ctr, data = data)
  lm_summary <- summary(lm_model)
  
  # Extract p-value from the linear regression summary
  p_value <- lm_summary$coefficients[2, 4]  # p-value for the ctr coefficient
  
  # Return results as a list: p-value and effect size (mean of sales - intercept)
  effect <- mean(sales) - mean(0.2)  # Mean effect (this could be adjusted based on the specific model)
  
  return(list(effect_size = effect, p_value = p_value))
}


```

##### Analysis

```{r q3_scenario1_analysis}

null_results <- run_simulations(effect_size = 0)        # No effect scenario

```


#### Scenario 2:  An Expected Effect

  2. Alternative Hypothesis: There is a positive relationship between click through rates and sales behavior on beauty products with the clean beauty labels “non-toxic” or “sustainable packaging”.  

##### Analysis

```{r q3_scenario2_analysis}

effect_results <- run_simulations(effect_size = 0.25)  # 25% increase scenario

# Create results table
results_table <- tibble(
  `Research Question` = c("Question 3", "Question 3"),
  Scenario = c("No Effect", "Effect: CTR Results in a 25% Increase in Purchase Behavior"),
  `Mean Effect in Simulated Data` = c(
    sprintf("%.2f", null_results$mean_effect),
    sprintf("%.2f", effect_results$mean_effect)
  ),
  `95% Confidence Interval of Mean Effect` = c(
    sprintf("(%.2f, %.2f)", null_results$ci_lower, null_results$ci_upper),
    sprintf("(%.2f, %.2f)", effect_results$ci_lower, effect_results$ci_upper)
  ),
  `Percentage of False Positives` = c(
    sprintf("%.1f%%", null_results$false_positives),
    "N/A"
  ),
  `Percentage of True Negatives` = c(
    sprintf("%.1f%%", null_results$true_negatives),
    "N/A"
  ),
  `Percentage of False Negatives` = c(
    "N/A",
    sprintf("%.1f%%", effect_results$false_negatives)
  ),
  `Percentage of True Positives` = c(
    "N/A",
    sprintf("%.1f%%", effect_results$true_positives)
  )
)

# Display the results table
kable(results_table, caption = "Simulation Results for Research Question 3", align = "c") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))




```






## References

**Authors (Names and Percentages)**: Maya Patel (20%), Tess Ibrahimchah (20%), Sara Shreim (20%), Depali Kulkarni (20%) & Suhasini Singh (20%)

   1. Schnell, A. (2022, October 13). Chi-Square Test of Independence Rule of Thumb: n > 5. The Analysis Factor. https://www.theanalysisfactor.com/chi-square-test-of-independence-rule-of-thumb/#:~:text=How%20Many%20Observations%20Does%20a,of%20each%20row%20and%20column.

   2. Lavuri, R., Chiappetta Jabbour, C. J., Grebinevych, O., & Roubaud, D. (2022). Green factors stimulating the purchase intention of innovative luxury organic beauty products: Implications for Sustainable Development. Journal of Environmental Management, 301, 113899. https://doi.org/10.1016/j.jenvman.2021.113899 

   3. Mou, J., Zhu, W., & Benyoucef, M. (2019). Impact of product description and involvement on purchase intention in cross-border e-commerce. Industrial Management; Data Systems, 120(3), 567–586. https://doi.org/10.1108/imds-05-2019-0280 

   4. Grappe, C. G., Lombart, C., Louis, D., & Durif, F. (2022). Clean labeling: Is it about the presence of benefits or the absence of detriments? consumer response to personal care claims. Journal of Retailing and Consumer Services, 65, 102893. https://doi.org/10.1016/j.jretconser.2021.102893 

   5. Shim, J., Woo, J., Yeo, H., Kang, S., Kwon, B., Lee, E. J., Oh, J., Jeong, E., Lim, J., & Park, S. G. (2024). The Clean Beauty Trend among Millennial and Generation Z consumers: Assessing the safety, ethicality, and sustainability attributes of cosmetic products. SAGE Open, 14(2). https://doi.org/10.1177/21582440241255430
